On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-06-24 documents/paper.tex
RSI

A correction factor due to the staggered magnetic field of the Yee lattice should be introduced;  Their $Z_2$ equation (correcting for spatial inaccuracies, but not temporal) was sufficient.

@@

>>>>

A correction factor due to the staggered magnetic field of the Yee lattice should be introduced; [Fang 1994]. Their $Z_2$ equation (correcting for spatial inaccuracies, but not temporal) was sufficient.

@@

The type of feed-port may affect the convergence rate by introducing unphysical transients.

Simply monitoring the source current during the simulation is deceptive. Periodically monitoring the fourier transform
